Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Mechanical Perturbations

### 2024-06-27 main.tex
Remove duplicate paragraph

The magnitude of the perturbation is determined using an adaptive staircase
procedure.  \todo{Cite to correct paper from thesis} The adaptive staircase
takes the nominal fall threshold as input and randomly chooses one of five
possible forces that are centred around the nominal fall threshold with
10~\si{\newton} intervals. If the perturbation results in a fall, the nominal
fall threshold is decreased with 10~\si{\newton}. If the perturbation does not
results in a fall, the nominal fall threshold is increased with
10~\si{\newton}. This adaptive staircase procedure ensures that approximately
50\% of the perturbations applied to the rider result in a fall.
%
\begin{figure}
  \centering
  \subcaptionbox{Start}{\includegraphics[width=40mm]{figures/start.png}}
  \subcaptionbox{During}{\includegraphics[width=40mm]{figures/during.png}}
  \subcaptionbox{After}{\includegraphics[width=40mm]{figures/after.png}}
  \subcaptionbox{Recovery}{\includegraphics[width=40mm]{figures/recovery.png}}
  \caption{Video frames depicting the application of a perturbation and the
  rider's response and recovery.}
  \label{fig:perturbation-sequence}
\end{figure}

>>>>

%
\begin{figure}
  \centering
  \subcaptionbox{Start}{\includegraphics[width=40mm]{figures/start.png}}
  \subcaptionbox{During}{\includegraphics[width=40mm]{figures/during.png}}
  \subcaptionbox{After}{\includegraphics[width=40mm]{figures/after.png}}
  \subcaptionbox{Recovery}{\includegraphics[width=40mm]{figures/recovery.png}}
  \caption{Video frames depicting the application of a perturbation and the
  rider's response and recovery.}
  \label{fig:perturbation-sequence}
\end{figure}
